D3064R0: Bringing the Laws of Physics, Computer-System Constraints, and Compilers to Bear on the OOTA Problem

### 2024-02-14 ootavacuous.tex
executions: Add roadmap
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

>>>>

The following sections look at semantic-dependency complications that
can arise in the context of executions.
Section~\ref{sec:Executions Can Be Merged}
shows that executions can be merged,
Section~\ref{sec:Executions Depend on Context}
shows that executions depend on context,
Section~\ref{sec:Executions Can Be Nondeterministic}
looks at nondeterministic executions,
Section~\ref{sec:Executions Can Be Complex}
looks at complex executions,
Section~\ref{sec:Implementers and Users Influence the Definition of Execution}
describes how implementers and users (not just the standard!) can
influence executions,
and finally
Section~\ref{sec:So What Exactly is an Execution, Anyway?}
summarizes this material in preparation for bringing the real world
to bear on these issues.
